\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumerate}

\begin{document}

\begin{tabular}{|c|c|}
\hline
Slot & Question \\\hline
``add\_pizza" & ``What specialty pizza would you like?"\\\hline
``change\_size" & ``What size? (small,medium,large)"\\\hline
``change\_crust" & ``What type of crust?"\\\hline
``delivery\_type" & ``Pick-up or delivery?"\\\hline
``get\_address" & ``What is your address?"\\\hline
``add\_name" & ``Can I get a name for the order?"\\\hline
``add\_phone" & ``Can you give us a phone number?"\\\hline
``check\_order" & ``Got your order. Is this correct?"\\\hline
``misunderstood\_pizza" & ``I'm sorry, here's what you asked for \_\_\_. Should we restart this pizza?"\\\hline
``past\_customer" & ``Would you like to reorder your preferred pizza?"\\\hline
``order\_check" & ``Would you like to see your estimated wait time?"\\\hline
\end{tabular}

Our system is able to take some dynamic input but expects certain input for some fields.
How to use our system\:
-cancel
In order to cancel, type cancel at any time

-repeat
Repeats the last thing the machine said

-querying for order status
In order to query your order status, type status.
Currently it prompts for a phone number, only 1234567890 works right now.

-ordering a single specialty pizza:
Specialty pizzas --> ["vegan", "hawaiian", "meat lovers", "4 cheese", "pepperoni", "veggie supreme"]
Sizes --> ["small", "medium", "large"]
Crusts --> ["thin", "regular", "gluten-free", "deep-dish"]
Names --> ["Jessica", "Devin", "Alex", "Alexandra"]

-reordering the preferred order
Type reorder at anytime to reorder. Currently the only acount we have corresponds to the phone number 1234567890

-provide information out-of-turn or out-of-order
You are able to type multiple pieces of information at once as well as in any order, the system will prompt you for what it still needs.

-revise previous information
You are able to change anything within the keywords listed above at any time.
i.e.) I want a hawaiian pizza --> Oh wait I want a vegan
This will change your pizza from hawaiian to vegan

-reject previously provided informatino
You can type start over at any time to start over.
The system also confirms your order with you, to which you can type no and reject that information.
You can also reorder and reject the information that was saved.

\end{document}
